\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}

\geometry{margin=2.5cm}

\titleformat{\section}{\Large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries}{\thesubsection}{1em}{}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    pdftitle={Interview Questions - Careers after BUT GIM},
    pdfauthor={BUT Industrial Engineering and Maintenance}
}

\begin{document}

\title{\textbf{Interview Question List} \\
\large Teacher-Researchers \\
\normalsize Careers after BUT Industrial Engineering and Maintenance}
\author{Rong ZHOU - University of Lorraine}
\date{\today}

\maketitle

\vspace{0.5cm}

\section{Career Path and Professional Experience}

\begin{enumerate}[leftmargin=*]
    \item Could you briefly introduce your career path and your current research field?

\end{enumerate}

\section{Required Qualities and Skills}

\begin{enumerate}[leftmargin=*]
    \item Based on your experience, what are the main essential human qualities for teacher-researchers?

    \item What technical skills do you consider essential in your field, and how do you recommend acquiring or deepening them?

    \item What transferable skills (communication, project management, teamwork, etc.) are particularly valued? Can you provide concrete examples?

    \item Are there any other skills, formal or informal, that you consider important for success in this role?
\end{enumerate}

\section{Personal Experience and Daily Professional Life}

\subsection{Typical Day}

\begin{enumerate}[leftmargin=*]
    \item Can you describe a typical day in your job as a teacher-researcher?

    \item What is the approximate distribution of your time between teaching, research, administration, and other activities?

    \item What types of interactions do you have on a daily basis (with students, colleagues, industry professionals, etc.)?
\end{enumerate}

\subsection{Feelings and Reflections}

\begin{enumerate}[leftmargin=*]
    \item What do you appreciate most about your work and what motivates you on a daily basis? Can you illustrate with a concrete example?

    \item What are, in your opinion, the most difficult aspects of your profession, and how do you manage them?

    \item How would you describe your workload? Is it generally balanced or subject to intense periods? How do you manage them?
    
    \item What is the balance between professional and personal life in your profession and what strategies do you use to preserve it?
    
    \item What are the main sources of satisfaction in your work?
    
    \item Do you encounter particular difficulties or frustrations? If so, what approaches or resources do you recommend to overcome them?
\end{enumerate}

\section{Possible Career Developments}

\begin{enumerate}[leftmargin=*]
    \item What are the main possible career developments for a teacher-researcher?

    \item Do you know of teacher-researchers who have evolved to other professions (scientific mediator, R\&D engineer, consultant, etc.)?

    \item What additional training or qualifications are necessary to progress in an academic career?
\end{enumerate}

\section{From BUT GIM to the Teacher-Researcher Profession: Advice and Perspectives}

\begin{enumerate}[leftmargin=*]
    \item What advice would you give to a student from a BUT GIM who wishes to pursue a career as a teacher-researcher? (skills to develop, experiences to prioritize, steps to take)

    \item Are there any important elements that we have not discussed and that you would like to share to help students in their professional project?
\end{enumerate}

\vspace{1cm}

\section*{}

Thank you very much for your participation and the time you dedicate to this interview. Your answers will be invaluable in guiding students in their career choices.

\vspace{0.5cm}

\noindent\rule{\textwidth}{0.4pt}

\vspace{0.3cm}

\noindent\textit{Interview date: \underline{\hspace{4cm}}}

\noindent\textit{Name of the teacher-researcher: \underline{\hspace{6cm}}}

\noindent\textit{Institution: \underline{\hspace{8cm}}}

\end{document}
